Astr 513: Final Project

### 2016-05-07 Final_Project/ms.tex
Updated captions.

\subsection{Likelihood}
\label{sec:likelihood}
Using the above model for the distance modulus allows us to write a
probability that a model can generate our data:
%
%\begin{equation}
\begin{align}
  \label{eq:likelihood}
  P(\mu(z)|\mathrm{cosmo}) &= \frac{1}{\sqrt{2\pi|\mathbf{C}|}}\nonumber \\
  &\qquad{}\exp\left[-\frac{1}{2} \sum_{i,j=0}^{N_{samples}}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_i 
    \mathbf{C}^{-1}_{i,j}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_j\right]
\end{align}
%\end{equation}
%
where $\mathbf{C}$ is the full covariance matrix between all of the $N_{samples}$ 
in the data, and $\mathrm{cosmo}$ represents the cosmology that we are investigating
(e.g. flat $\Lambda$CDM, $w$CDM, etc.). 
This is not the full picture though, since we must employ
Bayes' Theorum in order to include any priors on our choice of 
parameters and recover the posterior distribution function of our
parameters given our data
%
\begin{equation}
  \label{eq:posterior}
  P(\mathrm{cosmo}|\mu(z)) = P_{prior}(\mathrm{cosmo}) P(\mu(z)|\mathrm{cosmo}).
\end{equation}
%
For this work we investigate a combination of priors. \CosmoSIS is implemented
in a way that requires the user to provide bounds on the parameter space, which we
detail for each parameter in \autoref{tab:priors}
Within those bounds, we investigated using a flat prior $P_{prior}=1$ and
\Planck priors.

@@

\begin{figure}
  \label{fig:planck_corner}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/corner_example.eps}
  \caption{\TM{THIS IS A PLACE HOLDER PLOT!}
    Posterior distributions of the cosmological parameter
    analysis using just the \Planck likelihood. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
\end{figure}

\subsection{CosmoSIS}
\label{sec:CosmoSIS}
\LC{I'll write more later if need be.}
\CosmoSIS is a framework that connects multiple existing codes as 
modules in order to do cosmological parameter estimation. Users 
can utilize existing codes or use their own codes for modules. For 
our analysis, \CosmoSIS provides a convenient way to link together 
CAMB, the \Planck likelihood code (our priors), and our {\sn} likelihood 
code in a single pipeline. This design choice minimized the significant
time that would inevitably have been spent on connecting these 
independently-made programs into one, allowing us to focus on 
doing science rather than software development.

@@

\EW{Just a filler for the table for the wCDM fits}
\begin{table}[h]
  \label{tab:wcdm}
  \centering
  \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & 0                      & 0     & 0     \\
    Betoule et al. (no priors) & 0                      & 0     & 0     \\
    Rest et al.                & 0                      & 0     & 0     \\
    Rest et al. (no priors)    & 0                      & 0     & 0     \\
  \end{tabular}
  \caption {Posterior distirbutions of parameters in the
    wCDM model. Uncertainties denote symmetrized 68\%
    confidence intervals maginalized over other parameters.}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{Betoule2014} data without including the
    \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_noprior_corner}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{Betoule2014} data including the
    \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_withprior_corner}
\end{figure}

>>>>

\subsection{Likelihood}
\label{sec:likelihood}
Using the above model for the distance modulus allows us to write a
probability that a model can generate our data:
%
\begin{align}
  \label{eq:likelihood}
  P(\mu(z)|\mathrm{cosmo}) &= \frac{1}{\sqrt{2\pi|\mathbf{C}|}}\nonumber \\
  &\qquad{}\exp\left[-\frac{1}{2} \sum_{i,j=0}^{N_{samples}}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_i 
    \mathbf{C}^{-1}_{i,j}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_j\right]
\end{align}
%
where $\mathbf{C}$ is the full covariance matrix between all of the $N_{samples}$ 
in the data, and $\mathrm{cosmo}$ represents the cosmology that we are investigating
(e.g. flat $\Lambda$CDM, $w$CDM, etc.). 
This is not the full picture though, since we must employ
Bayes' Theorum in order to include any priors on our choice of 
parameters and recover the posterior distribution function of our
parameters given our data
%
\begin{equation}
  \label{eq:posterior}
  P(\mathrm{cosmo}|\mu(z)) = P_{prior}(\mathrm{cosmo}) P(\mu(z)|\mathrm{cosmo}).
\end{equation}
%
For this work we investigate a combination of priors. \CosmoSIS is implemented
in a way that requires the user to provide bounds on the parameter space, which we
detail for each parameter in \autoref{tab:priors}
Within those bounds, we investigated using a flat prior $P_{prior}=1$ and
\Planck priors.

@@

\begin{figure}
  \label{fig:planck_corner}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/corner_example.eps}
  \caption{\TM{THIS IS A PLACE HOLDER PLOT!}
    Posterior distributions of the cosmological parameter
    analysis using just the \Planck likelihood. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
\end{figure}

\subsection{CosmoSIS}
\label{sec:CosmoSIS}
\CosmoSIS is a framework that connects multiple existing codes as 
modules in order to do cosmological parameter estimation. Users 
can utilize existing codes or use their own codes for modules. For 
our analysis, \CosmoSIS provides a convenient way to link together 
CAMB, the \Planck likelihood code (our priors), and our {\sn} likelihood 
code in a single pipeline. This design choice minimized the significant
time that would inevitably have been spent on connecting these 
independently-made programs into one, allowing us to focus on 
doing science rather than software development.

@@

\EW{Just a filler for the table for the wCDM fits}
\begin{table}[h]
  \label{tab:wcdm}
  \centering
  \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & 0                      & 0     & 0     \\
    Betoule et al. (no priors) & 0                      & 0     & 0     \\
    Rest et al.                & 0                      & 0     & 0     \\
    Rest et al. (no priors)    & 0                      & 0     & 0     \\
    \Planck likelihood only    & 0                      & 0     & 0     \\
  \end{tabular}
  \caption {Posterior distirbutions of parameters in the
    wCDM model for both data sets and the \Planck likelihood only. 
    Uncertainties denote symmetrized 68\%
    confidence intervals maginalized over other parameters.}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{Betoule2014} data without including the
    \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_noprior_corner}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{Betoule2014} data including the
    \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_withprior_corner}
\end{figure}
